% template for papers with a title page
% see dgstpp.sty for title page info
% format: latex
% last changed: 1 Apr 2015

\documentclass[11 pt]{IEEEtran}

% standard math packages
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{scrextend}
\usepackage{tikz}
\usepackage{hyperref}
\usetikzlibrary{arrows, shapes, plothandlers}
\usepackage{tikz}
\usepackage{tikzscale}
\usepackage{ragged2e}
\usepackage{hyperref}


\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=bash,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breakatwhitespace=true,
  tabsize=3,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}


% Phil Parker's DGS packages, some modified
\usepackage{remexpp,pprroof,dgstpp}

% other packages
\usepackage{setspace}
%\usepackage{hyperref,color}

% "fancy" font
\usepackage{fourier}
\usepackage[T1]{fontenc}
   
% make reference header the right font size
\renewcommand\refname{\Large References}
   
% theorems, remarks, etc using Phil Parker's "remexpp.sty"
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newremark{definition}[theorem]{Definition}
\newremark{example}[theorem]{Example}
\newremark{remark}[theorem]{Remark} 

% make rsfs, TeX \cal, and Euler script *all* available
\usepackage{mathrsfs}
\let\rscr=\mathscr
\let\mathscr=\relax
\let\mcal=\mathcal
\usepackage{eucal}
\let\escr=\mathcal
\let\mathcal=\relax

% commutative diagrams with XY-pic
\usepackage[all]{xy}
\SelectTips{cm}{}

\arraycolsep .2em
   
% new commands
\renewcommand{\a}{\alpha}
\newcommand{\Aut}[1]{\textrm{Aut}(#1)}
\newcommand{\B}{\rscr{B}}
\newcommand{\br}[2]{\left[#1,#2\right]}
\newcommand{\bre}{\br{\ }{\,}}
\newcommand{\ddg}{\ddot{\g}}
\newcommand{\dg}{\dot{\g}}
\newcommand{\DGS}{D{\kern-.375em}G{\kern-.2em}S}
\newcommand{\ds}{\oplus}
\newcommand{\eB}{\escr{B}}
\newcommand{\eH}{\escr{H}}
\newcommand{\eI}{\escr{I}}
\newcommand{\eV}{\escr{V}}
\newcommand{\g}{\gamma}
\newcommand{\G}{\Gamma}
\newcommand{\h}{\lal{h}}
\renewcommand{\H}{\rscr{H}}
\newcommand{\hp}{\h_{2p + 1}}
\newcommand{\iso}{\cong}
\newcommand{\lag}{\mathfrak{g}}
\newcommand{\lal}[1]{\mathfrak{#1}}
\newcommand{\n}{\lal{n}}
\newcommand{\pplus}{+\mspace{-10 mu}+}
\newcommand{\R}{\mathbb{R}}
\newcommand{\rS}{\rscr{S}}
\renewcommand{\span}[1]{[\mspace{-3.25 mu}[ #1 ]\mspace{-3.25 mu}]}
\newcommand{\surj}{\rightarrow\kern-.82em\rightarrow}
\newcommand{\tQ}{\widetilde{Q}}
\renewcommand{\v}{\lal{v}}
\newcommand{\V}{\rscr{V}}
\newcommand{\z}{\lal{z}}
%%Alex's defined commands%%
\newcommand{\adx}{ad$_x$ }
\newcommand{\ady}{ad$_y$ }
\newcommand{\adz}{ad$_z$ }
\newcommand{\fj}{\mathfrak{j}}
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\fz}{\mathfrak{z}}
\newcommand{\fv}{\mathfrak{v}}
\newcommand{\fh}{\mathfrak{h}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\FF}{\mathbb{F}}

\makeatletter
\newcommand{\ad}[1]{\mathop{\operator@font ad}\nolimits_{#1}}
\makeatother

% show labels in margin (must be last package added)
\usepackage{showlabels}

% input information for the title page here:
\preprint{}
\title{Apache Apex}
\author{Alexander Jansing}
\address{
   Computer Science Department\\
   State University of New York,\\
   Polytechnic Institute\\
   Utica, NY 13502\\
   USA\\
   \textsf{jansina@sunyit.edu}
}
\date{\today}
\abstract{
Apache Apex is Hadoop YARN-native framework for building distributed applications and applies native streaming to the data processing pipeline \cite{WEISE}. The Apex project was mainly been driven by the company DataTorrent. DataTorrent shut its doors back in May of 2018\cite{WIKI}\cite{DATANAMI}.

This project is designed to help other developers write their own Apache Apex applications by providing an docker image with Apex, JDK8, and Maven installed. The start-up script provided can be easily changed so that others can pass their project directory as a volume to a container and rapid testing can be performed.
}
\msc{}{}

\begin{document}
\maketitle


% Your paper must be structured properly (with numbered titled sections), detailing
%   the main focus of the project (the topic)
%   the relevance of the topic to big data (whether or not your topic is directly related to Spark,
%  and Hadoop)
%   the challenges in using the software relevant to your topic (installation, etc.)
%   the work you have actually done for the project (code, etc.)
%   your self-evaluation (what you managed to accomplish and what you failed to complete)
%   the references you have used (books, papers, web sites, etc.); remember that you must
%  give proper credits (i.e. proper references) to work you use that is not your own.

\section{Introduction}
\subsection{Apache Apex and Mahlar}
Apache Apex is Hadoop YARN-native framework for building distributed applications and applies native streaming to the data processing pipeline \cite{WEISE}. The Apex project was mainly been driven by the company DataTorrent. DataTorrent shut its doors back in May of 2018\cite{WIKI}\cite{DATANAMI}. The last release of Apex was put out on April $27^{th}$ of the same year; which wasn't that long ago as of the writing of this paper, but looking at the related github repositories doesn't do much to inspire confidence in future releases.

Apex comes with Malhar, a codec library of operators used to enable users to speed up their work and in a variety of languages (Java, JavaScript, Python, R, Ruby). Malhar operations are based off of templates and can be easily extended to perform the actions you need. Additionally, Malhar allows the developer to change the properties of an operator at runtime, so the application doesn't need to be brought offline\cite{MALHAR}.

This project is designed to help other developers write their own Apache Apex applications by providing an docker image with Apex, JDK8, and Maven installed. The start-up script provided can be easily changed so that others can pass their project directory as a volume to a container and rapid testing can be performed.

\subsection{Structure of the Paper}
In this preliminary report, I will quickly go over what I have done:
\begin{enumerate}
\item to research the topic,
\item with the Apache Apex framework,
\item what I think the framework is good for and how it relates to our coursework so far,
\item what I think I can do with the software in the remainder of the semester,
\item and any work that is either a stretch goal or will be set aside for future projects.
\end{enumerate}
 

\section{Research}
Whenever researching a piece of technology to use, especially when software under Apache Software Foundation (\emph{ASF}, plenty of documentation is available on the project's site. Usually, there is enough information there to get started in understanding how and why to use a particular product. Usually one should look beyond the product's page when the software isn't under the ASF; as many companies are looking to sell a license.

In the case of this project, I used the Apache Apex project page\cite{APEX}, the provided ReadTheDocs pages\cite{APEXrtd_dt}\cite{APEXrtd_apache}\cite{MALHAR}, a presentation from a DataTorrent employee, Thomas Weise\cite{WEISE}, Wikipedia and its references\cite{WIKI}\cite{DATANAMI}.
 
 \section{Using Apex}
TODO


\newpage
\section{Appendix}
 
\subsection{Code snippets and links}
\begin{enumerate}
\item MapReduce - \url{https://github.com/apjansing/apex-maven/tree/master/src/MapReduce}
\item apex-maven 
\begin{enumerate}
  \item \url{https://github.com/apjansing/apex-maven/blob/master/src/docker/Dockerfile}
  \item \url{https://hub.docker.com/r/apjansing/apex-maven/}
\end{enumerate}

\item pull\_and\_start\_dev\_apex\_docker.sh
\begin{lstlisting}
  #!/bin/bash
  JANSING_PROJECT_HOME=`(git rev-parse --show-toplevel)`
  JANSING_REPO_NAME=`(basename $JANSING_PROJECT_HOME)`
  
  docker pull apjansing/apex-maven
  docker run -it --name=apex -v $JANSING_PROJECT_HOME:/home/apex/ $JANSING_REPO_NAME -p 50070:50070 -p 8089:8088 apex-maven
\end{lstlisting}

 \item MapReduce Output
\begin{lstlisting}
  {monstrous=1, allah=1, xlv=1, xxxvii=1, bag=1, dutch=1, xxiv=1, vii=3,...},
  {... cheerless=1, monstrous=4, flinty=1, been=12, gaping=1, ...},
  {... ticking=1, monstrous=1, been=64, mostly=2, ...},
  {... account=5, monstrous=6, been=60, unquestion=1, ...}
\end{lstlisting}
 \end{enumerate}


 \subsection{Source locations}
 
 \subsubsection{Apex Documentations}
 \begin{enumerate}
 \item[] \url{http://apex.apache.org/docs/apex/apex_development_setup/#creating-new-apex-project}
 \end{enumerate}

 \subsubsection{Github Repositories}
 \begin{enumerate}
  \item[] \url{https://github.com/apjansing/apex-maven}
	\item[] \url{https://github.com/apache/apex-core}
	\item[] \url{https://github.com/apache/apex-malhar}
	\item[] \url{https://github.com/apache/apex-site}
 \end{enumerate}

\subsubsection{Apache Apex Downloads}
\begin{enumerate}
	\item[] \url{http://apex.apache.org/downloads.html}
	\item[] \url{https://hub.docker.com/r/apacheapex/sandbox/}
\end{enumerate}
  
\begin{thebibliography}{99}
\bibitem{APEX}
Foundation, A. (2018). Apache Apex. [online] Apex.apache.org. Available at: \url{https://apex.apache.org/} [Accessed 5 Nov. 2018].

\bibitem{WIKI}
En.wikipedia.org. (2018). Apache Apex. [online] Available at: \url{https://en.wikipedia.org/wiki/Apache_Apex [Accessed 10 Nov. 2018]}.

\bibitem{WEISE}
Weise, T. (2016). Architectual Comparison of Apache Apex and Spark Streaming. [online] Available at: \url{https://www.slideshare.net/ApacheApex/architectual-comparison-of-apache-apex-and-spark-streaming} [Accessed 10 Nov. 2018].

\bibitem{APEXrtd_dt}
Dt-docs.readthedocs.io. (2018). Beginner's Guide - DataTorrent Documentation. [online] \url{Available at: https://dt-docs.readthedocs.io/en/latest/beginner/} [Accessed 10 Nov. 2018].

\bibitem{APEXrtd_apache}
Apex.apache.org. (2018). Apache Apex Documentation. [online] Available at: \url{http://apex.apache.org/docs/apex/} [Accessed 10 Nov. 2018].

\bibitem{MALHAR}
Apex.apache.org. (2018). Apache Apex Malhar Documentation. [online] Available at: \url{http://apex.apache.org/docs/malhar/} [Accessed 10 Nov. 2018].

\bibitem{DATANAMI}
Leopold, G. (2018). DataTorrent, Stream Processing Startup, Folds. [online] Datanami. Available at: \url{https://www.datanami.com/2018/05/08/datatorrent-stream-processing-startup-folds/} [Accessed 10 Nov. 2018].
\end{thebibliography}
\end{document}






















